Boutiques: a flexible framework for automated application integration in computing platforms

### 2017-10-11 boutiquespaper.tex

\author{Tristan Glatard, Tristan Aumentado-Armstrong, Natacha Beck, Pierre Bellec,\\
        Remi Bernard, Sorina Camarasu-Pop, Fr\'ed\'eric Cervenansky, Samir Das, \\
        Rafael Ferreira da Silva, Guillaume Flandin, John Flavin, Pascal Girard, \\
        Krzysztof J. Gorgolewski, Gregory Kiar, Charles G. Guttmann, Nathaniel Kofalt, \\
        Pierre-Olivier Quirion, Pierre Rioux, Marc-\'Etienne Rousseau, Gunnar Schaeffer, Alan C. Evans}
\maketitle

@@

A few MRtrix3\footnote{\url{http://www.mrtrix.org/}} tools were also make available in VIP. 
A script developed at Creatis, which combines MRtrix3 and FSL tools, is currently being
imported and tested.

\todo{Tristan: validate the descriptions above}

\begin{table}
  \begin{tabular}{l|ccccccc}
    \rowcolor[gray]{0.9}
    Application                      & \multicolumn{7}{c}{Input/Output properties} \\
    \rowcolor[gray]{0.9}
                                     & Dependencies      &Groups             & Lists             & Optional          &Default            & Enum              & Min/max\\

>>>>

\author{Tristan Glatard, Tristan Aumentado-Armstrong, Natacha Beck, Pierre Bellec,\\
        Remi Bernard, Sorina Camarasu-Pop, Fr\'ed\'eric Cervenansky, Samir Das, \\
        Rafael Ferreira da Silva, Guillaume Flandin, John Flavin, Pascal Girard, \\
        Krzysztof J. Gorgolewski, Charles G. Guttmann, Gregory Kiar, Nathaniel Kofalt, \\
        Pierre-Olivier Quirion, Pierre Rioux, Marc-\'Etienne Rousseau, Gunnar Schaeffer, Alan C. Evans}
\maketitle

@@

A few MRtrix3\footnote{\url{http://www.mrtrix.org/}} tools were also made available in VIP, as well as 
a script developed at Creatis, which combines MRtrix3 and FSL tools.

A few other applications from the FLI (France Life Imaging) consortium were also imported in
VIP using Boutiques. One of them is Ginfizz, a FMRI pipeline allowing to execute multiple 
preprocessing steps and basic analyses such as: (i) realignment (motion registration and correction),
(ii) slice timing (temporal interpolation to correct for the delay of acquisition between slices), 
(iii) coregistration (registering functional and structural data), (iv) normalization (registering 
of functional and anatomical data to a match a template that has to be specified), and (iv)
smoothing (spatial filtering to increase Signal to Noise ratio). The use of Docker containers (\url{https://hub.docker.com/r/fliiam/ginfizz} based on \url{https://hub.docker.com/r/miykael/nipype_level2}) 
greatly simplifies its deployment. The animaN4BiasCorrection tool from the Anima  \footnote{\url{https://github.com/Inria-Visages/Anima-Public/wiki}} project was also made available 
in VIP. The import process was straightforward.

\note{sorina}{@tristan: please check if you agree with the descriptions above}

\begin{table}
  \begin{tabular}{l|ccccccc}
    \rowcolor[gray]{0.9}
    Application                      & \multicolumn{7}{c}{Input/Output properties} \\
    \rowcolor[gray]{0.9}
                                     & Dependencies      &Groups             & Lists             & Optional          &Default            & Type restriction             & Min/max\\
